MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-02-20 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
note correct branch

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

>>>>

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL
